---
title: "Part5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5. A tutorial for my_rf_cv

```{r}
# load my_rf_cv method
source("../../stat302proj2/R/my_rf_cv.R")
# load my_penguins dataset
load("../Data/my_penguins.rda")
```

```{r}
library(ggplot2)
library(dplyr)
library(randomForest)
library(stats)
library(class)
library(magrittr)
# create a data frame to store CV estimated MSE for each k
df_cv_MSE <- data.frame(integer(), double())
for (i in 1:30) {
  df_cv_MSE <- rbind(df_cv_MSE, c(2, my_rf_cv(2))) 
  df_cv_MSE <- rbind(df_cv_MSE, c(5, my_rf_cv(5)))
  df_cv_MSE <- rbind(df_cv_MSE, c(10, my_rf_cv(10)))
}
# assign column names to the data frame
colnames(df_cv_MSE) <- c("k", "CV_estimated_MSE")
# factorize k
df_cv_MSE$k <- as.factor(df_cv_MSE$k)
# make a boxplot to show the distribution of CV estimated MSE for each k
ggplot(df_cv_MSE, aes(x = k, y = CV_estimated_MSE, color = k)) +
  geom_boxplot(fill='#A4A4A4')+
  labs(title="Plot of CV estimated MSE by k",x="k(number of folds)", y = "CV estimated MSE") +
  theme_bw()
# save the visualization to Figures folder
ggsave("boxplot.png", path = "../Output/Figures", height=9,width=12,dpi=72)
```


```{r}
library(tibble)
library(dplyr)
library(readr)
# extract CV estimated MSE with k = 2
k_2 <- filter(df_cv_MSE, k==2)[["CV_estimated_MSE"]]
# extract CV estimated MSE with k = 5
k_5 <- filter(df_cv_MSE, k==5)[["CV_estimated_MSE"]]
# extract CV estimated MSE with k = 10
k_10 <- filter(df_cv_MSE,k==10)[["CV_estimated_MSE"]]
# create a summary table for average CV estimates and the standard deviation of CV estimates 
sum_table <- rbind(c(mean(k_2), sd(k_2)),
                   c(mean(k_5), sd(k_5)),
                   c(mean(k_10), sd(k_10)))
# assign row names to the table
sum_table <- cbind(paste0("k = ", c(2, 5, 10)), sum_table)
# assign column names to the table
colnames(sum_table) <- c("k", "average CV estimate", "sd of the CV estimates")
sum_table <- as_tibble(sum_table)
sum_table
# save the table of summary statistics to Results folder
saveRDS(sum_table, file = "../Output/Results/sum_table.rds")
# save the simulation results to Results folder
write_csv(df_cv_MSE, file = "../Output/Results/simulation.csv")
```

The boxplot shows that random forest model with higher number of folds will have lower CV estimated MSE and more concentrated distribution. The tables shows that random forest model with more folds will have lower average CV estimates and lower standard deviation of the cv estimates. This might be the case because as the number of folds incease, we are using more data to test each fold, making our prediction more accurate.